### 2021-06-18 manuscript.tex
update

@@

\emph{Oliveira, C. F. ; Benz-Navarrete, M. A. ; Breul, P. ; Tran, Q. A. ; Chevalier, B. ; Bacconnet, C. Assessment of small-strain modulus through wave velocity measurement with dynamic penetrometer Panda 3®. 6th International Confe- rence on Geotechnical and Geophysical Site Characterization, Budapest, Sep- tembre 2021. (Présentation orale).}

>>>>

\emph{Oliveira, C. F. ; Breul, P. ; Benz-Navarrete, M. A. ; Tran, Q. A. Essais de chargement dynamique et statique en pointe pénétrométrique : comparatifs au laboratoire. 37èmes Rencontres Universitaires de Génie Civil de l’AUGC, Sophia Antipolis, juin 2019.}

@@

\emph{Oliveira, C. F. ; Benz-Navarrete, M. A. ; Breul, P. ; Tran, Q. A. ; Chevalier, B. ; Bacconnet, C. Assessment of small-strain modulus through wave velocity measurement with dynamic penetrometer Panda 3®. 6th International Conference on Geotechnical and Geophysical Site Characterization, Budapest, Sep- tembre 2021. (Présentation orale).}
